% !TEX root = ozan_sener_thesis.tex

Robotics systems are typically composed of many sub-systems and these systems are developed in isolation. Moreover, robots learn continuously after deployment using human feedback is isolation as well. Hence, one of the most critical problems in robotics is sharing knowledge among different robotic systems as well as robotics sub-systems in deployement. In this chapter, we introduce the knowledge-engine we developed which enables robotics systems to share knowledge among robotic platforms as well as robotics sub-systems. The knowledge-engine we developed can handle variety of modalities and domains. More importantly, the knowledge comes from a variety of sources including online knowledge bases, learned concepts from robotics research groups from all over the world as well as physical robotic experiments.

\noindent\textbf{Contributions of this chapter.} We developed this knowledge engine in collaboration with Saxena, Jain, Jami, Misra and Koppula, and we call it RoboBrain. Within the scope of this dissertation, I contributed to a large-scale distributed system architecture which can scale to thousands of videos, images and text files. For completeness, in this chapter we also describe the formal definition of knowledge-engine, the query language for accessing the knowledge and a various applications of RoboBrain. RoboBrain is available at: http://www.robobrain.me



\input{./papers/rb/intro}

\input{./papers/rb/relatedwork}


\input{./papers/rb/overview}


\input{./papers/rb/graph}



\input{./papers/rb/system}

\input{./papers/rb/query}
\input{./papers/rb/applications}


\input{./papers/rb/conclusions}